\documentclass[margin]{res}  
\usepackage{helvet}
\usepackage{hyperref}

\textheight=700pt

\begin{document}
\name{Mohammadreza Amani}


\address{
    \href{https://github.com/MohammadrezaAmani}{GitHub}
    \\\href{https://www.linkedin.com/in/mohammadreza-amani/}{LinkedIn}
    % \\\href{https://stackoverflow.com/users/15300704/mohammadreza}{StackOverFlow}
}

\address{
    \href{mailto:more.amani@yahoo.com}{Email}
    \\\href{tel:+989352462779}{+98-935-246-2779}
    \\\href{https://MohammadrezaAmani.github.io}{website}
}

\begin{resume}

\section{EDUCATION}
\textbf{PolyTechnic University of Technology (AmirKabir)}, Tehran, IRI\\
{\sl Bachelor of Science}, Computer Science, Dec 2020\hfill GPA: 3.6

%-------------------------------------------------------------------------------


%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}
\employer{Co-Founder and Developer}
\location{Tehran}
\dates{June 2023 - now }
\title{\textbf{Farmina}}
\begin{position}
AI-Based Assistant for Farmers and Gardeners include Django-Backend, INUI(React) frontend for website, INUI (react-native) frontend for Android and IOS and INUI (electron) for windows and Linux 
\end{position}

\employer{Back-End Developer}
\location{Tehran}
\dates{Nov 2023 - }
\title{\textbf{Clonet}}
\begin{position}
    Clonet is a website that gives stores a website. (Same as an online stores like Amazon, but with a focus on branding and not only selling goods.) which started working in 2023. I have cooperated with Clonet team as a backend developer.
    \\
    \url{https://clonet.shop}
\end{position}


\employer{Back-End Developer}
\location{Tehran}
\dates{Nov 2022 - Nov 2023}
\title{\textbf{Thrita-Tech}}
\begin{position}
Tritatech is an active institution in the field of physiotherapy and artificial intelligence, which is trying to improve the quality of medical services by providing many innovations. I have been working as the technical supervisor of the back-end and DevOps team at Triatech.
\end{position}

\employer{Back-End Developer}
\location{Tehran}
\dates{Feb 2022 - Nov 2022}
\title{\textbf{Prav-Sass}}
\begin{position}
Django Backend Developer for Prav-Sass Company
\end{position}


\employer{}
\location{Tehran}
\dates{Dec 2020 - }
\title{\textbf{FreeLancer}}
\begin{position}
    In addition, I have worked as a freelancer for many years on small and large projects, including the \url{https://sepanja.com/}, the Shopeton website, as well as many other projects, a list of which you can find in View the CV file.
\end{position}


\section{SKILLS}


\textbf{Back-End}: Django, DRF, FastAPI, Gin, Python, GO
\\
\\
\textbf{DevOps}: Docker, kubernetes, NginX, RabbitMQ, CICD
\\
\\
\textbf{DataBases}: PostgrSQL, MongoDB, MySQL, Redis, ORM, SQLite3
\\
\\
\textbf{Worked with}: Celery, Kafka, ELK Stack, React, JavaScript,\
                    TypeScript, bootstrap, Material Design,\
                    Flutter, FireBase, Dart, INUI, JSINUI, \
                    Numpy, Pandas, Scikit-learn, Matplotlib,\
                    PyTorch, Tensorflow, Keras, OpenCV, Hazm,\
                    PyQT5, PySide, SQLAlchemy, pyscopg2, MyPy,\ 
                    pytesseract, Flask, spaCy, Beautiful Soup,\
                    Celery, Scrapy, Plotly, PyYAML, gunicorn,\ 
                    Kivy, KivyMD, Java,JavaFX, C, C++, Julia, Vuejs,\
                    Angular, Next.js, React, Foundation, Rust
\\
\\

\section{VOLUNTARY ACTIVITIES}
\par

\employer{Member of Scientific Team}
\location{Tehran}
\dates{Mar 2023 - Jul 2023}
\title{\textbf{CS50x Iran}}
\begin{position}
CS50x Iran Harvard's Introduction to the intellectual enterprises of computer science and the art of programming in Iran
\end{position}

\employer{Member of Scientific Team}
\location{Tehran}
\dates{Dec 2021 - Aug 2022}
\title{\textbf{CWS}}
\begin{position}
CWS event is the second of the series of computer science and engineering which is planned and held by the 16th round of scientific association of mathematics and computer engineering faculty.
\end{position}
\employer{Back-End Developer}
\location{Tehran}
\dates{Dec 2022 - Jul 2023}
\title{\textbf{UNILAND}}
\begin{position}
Backend Developer in UniLand Project for AmirKabir University of Technology.
\end{position}
\\
\\
\\
%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{PROJECTS}
\par
\textbf{INUI}: 
Powerful and Highly Customizable Python FrameWork for UI, It's allow Back-End developer and everyone who knows python, write full Front-End of their application or websites using python Quickly.
\hfill \href{https://github.com/MohammadrezaAmani/INUI}{GitHub}

\par
\textbf{MiniGram}: 
Minigram is a simple version of the Instagram social network backend built using the Django framework.
\hfill \href{https://github.com/MohammadrezaAmani/Minigram}{GitHub}

\par
\textbf{Eccoma}: 
Eccoma is an online store website like Digikala or Amazon, implemented using the Django framework.
\hfill \href{https://github.com/MohammadrezaAmani/Eccoma}{GitHub}

\par
\textbf{LinCut}:
Lincut is a simple yet powerful Link Shortener service built with FastAPI. It allows you to shorten long URLs into concise, user-friendly links.
\hfill \href{https://github.com/MohammadrezaAmani/LinCut}{GitHub}

\par
\textbf{Pure-Messenger} 
CLI realtime chatapp written in pure python. (include Server and Client)
\hfill \href{https://github.com/MohammadrezaAmani/Python-Websocket-Chatapp}{GitHub}

\par
\textbf{Authystem} 
Authentication technology provides access control for systems by checking to see if a user's credentials match the credentials in a database of authorized users or a data authentication server.
\hfill \href{https://github.com/MohammadrezaAmani/Authystem}{GitHub}


\par
\textbf{Farmina}: 
AI-Based Assistant for Farmers and Gardeners include Django-Backend, INUI(React) frontend for website, INUI (react-native) frontend for Android and IOS and INUI (electron) for windows and Linux \hfill \href{https://github.com/MohammadrezaAmani/Farmina}{underDevelopment-not available}

\par
\textbf{Roomify}: 
reservation system Back-End via Django.
\hfill \href{https://github.com/MohammadrezaAmani/Roomify}{GitHub}

\par
\textbf{UNILAND}: 
A highly modular and diverse Telegram Bot for universities and institutions written in python. This is the effort of a group of eight CS students at AUT. \hfill \href{https://github.com/MohammadrezaAmani/UniLand}{GitHub}
\par
\textbf{US-Messenger}: 
US Messenger is a modern communication tool implemented using WebSockets and Django.
\hfill \href{https://github.com/MohammadrezaAmani/US-Messenger}{GitHub}

\par
\textbf{Mosic}: 
Music Player website written in GoLang
\hfill \href{https://github.com/MohammadrezaAmani/Mosic}{GitHub}
\par
\textbf{GoGrep}: 
Go implementation of Grep module in linux.
\hfill \href{https://github.com/MohammadrezaAmani/GoGrep}{GitHub}


\par
\textbf{AruShop}: 
Ecommerce Website written in django and INUI for Arukala shop
\hfill \href{https://github.com/MohammadrezaAmani/arushop}{GitHub}

\par
\textbf{Django Amazon clone}: 
Django Amazon Clone with INUI Front-End.
\hfill \href{https://github.com/MohammadrezaAmani/Django-Amazon-clone}{GitHub}. 
\par
\textbf{MA Share}: 
Powerful web-based file sharing and management software written with FastAPI, INUI and Python.
\hfill \href{https://github.com/MohammadrezaAmani/Ma-share}{GitHub}.

\par
\textbf{Mail Tracker}: 
powerful Python FastAPI mail and content tracker.
\hfill \href{https://github.com/MohammadrezaAmani/MailTracker}{GitHub}.

\par
\textbf{JBeautiful date}: 
Simple and nice python library for working with jalali date-time.
 \hfill \href{https://github.com/MohammadrezaAmani/Jbeautiful-date}{GitHub}.

\par
\textbf{Other project}: 
There is many projects available on my github, if you are interested in projects you can check them.
 \hfill \href{https://github.com/MohammadrezaAmani/}{My-GitHub}.

%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%	Interests
%-------------------------------------------------------------------------------
Updated in Nov 07 2023. feel free to contact me. 

\begin{tabular}{|p{4cm}|p{6cm}|}
    \hline
    \textbf{Name:} & Mohammadreza Amani \\
    \hline
    \textbf{Email:} & \href{mailto:more.amani@yahoo.com}{more.amani@yahoo.com}\\
    \hline
    \textbf{Phone:} & \href{tel:+989352462779}{+98-935-246-2779} \\
    \hline
    \textbf{Address:} & Vali Asr, Tehran, Iran \\
    \hline
    \textbf{Github:} & \href{https://github.com/MohammadrezaAmani}{github.com/MohammadrezaAmani} \\
    \hline
    \textbf{LinkedIn:} & \href{https://www.linkedin.com/in/mohammadreza-amani/}{linkedin.com/in/mohammadreza-amani}\\ 
    \hline
    \end{tabular}
%-------------------------------------------------------------------------------
\end{resume}

\end{document}